\documentclass{article}
\usepackage{xcolor}
\usepackage{hyperref}

\usepackage{enumitem}
\usepackage{wasysym}
\usepackage{geometry}
% Custom command for incorrect options
\newcommand{\incorrectOption}{\item[\textbf{\Circle}]}
% Custom command for correct option
\newcommand{\correctOption}{\item[\textbf{\CIRCLE}]}

\definecolor{darkgreen}{rgb}{0,0.8,0.3}
\definecolor{darkblue}{rgb}{0.00,0.00,0.55}

\begin{document}

\begin{center}
\rule{\textwidth}{.0075in} \\
\rule[3mm]{\textwidth}{.0075in}\\

Universidade do Algarve\hfill WireShark - Capturing Packets \hfill 2024\\[3ex]

{\Large\bf Lab \#3} \\[3ex]

 \textcolor{blue}{YourName} \hfill  
 \textcolor{blue}{PL3} \hfill
 \textcolor{blue}{YourStudentNumber}\\

\rule{\textwidth}{.0075in} \\
\rule[3mm]{\textwidth}{.0075in} \\
\end{center}



\begin{center}
\rule{\textwidth}{0.4pt}
\textbf{Completely fill the circles as shown: \Circle \Circle \CIRCLE \Circle}
\rule{\textwidth}{0.4pt}
\end{center}


\begin{enumerate}[leftmargin=*, label=\textbf{Q\arabic*}, itemsep=-5pt]
\item A new analyst has just joined a company and can't seem to see
  any packets coming through on Wireshark. What should be done to help
  the analyst? 
  \begin{enumerate}[itemsep=-3.5pt, label={}]
    \incorrectOption Add the analyst to the Wireshark permissions group (access
      control).
    \incorrectOption Have the analyst install Wireshark.
    \incorrectOption Have the analyst run Wireshark as {sudo}.
    \incorrectOption Have the analyst log in as {root}.
   \end{enumerate}   
  %
\item A team member is looking to capture traffic on the server. The
  team member says the traffic is visible, but the capture file cannot
  be saved. Which is a likely solution? 
  \begin{enumerate}[itemsep=-3.5pt, label={}]
  \incorrectOption Start capturing. 
  \incorrectOption Stop capturing.
  \incorrectOption Select the correct network.
  \incorrectOption Close the capture file.
  \end{enumerate}  
 
\item A colleague is working on observing only HTTPS packets from an
  existing file. Which filter should be used?  
  \begin{enumerate}[itemsep=-3.5pt, label={}]
  \incorrectOption Display filter with {http}. 
  \incorrectOption Display filter with {tcp.port==443}.
  \incorrectOption Capture filter with {tcp.port==443}.
  \incorrectOption Capture filter with {http}.
  \end{enumerate}
 
\item An analyst has been alerted of strange network activity coming
  from IP address 18.160.96.85 and has been tasked with locating all
  the packets containing the IP address in Wireshark capture. Which
  filter should be used?  
  \begin{enumerate}[itemsep=-3.5pt, label={}]
  \incorrectOption ip.addr=18.160.96.85
  \incorrectOption ip.src==18.160.96.85
  \incorrectOption ip.dst==18.160.96.85
  \incorrectOption ip.addr==18.160.96.85
\end{enumerate}

\item A server has a lot of traffic on a particular IP address. To
  observe other packets, the analyst just wants to see those packets
  not associated with IP address 18.160.96.85. Which filter should be used? 
  \begin{enumerate}[itemsep=-3.5pt, label={}]
  \incorrectOption !(ip.addr=18.160.96.85) or tcp.port==443
  \incorrectOption (ip.addr!=18.160.96.85) or tcp.port==443
  \incorrectOption !(ip.addr==18.160.96.85) and (tcp.port==443 or tcp.port==80)
  \incorrectOption (ip.addr!=18.160.96.85) and tcp.port==80
  \end{enumerate}
\end{enumerate}
\end{document}
