\documentclass{article}
\usepackage{xcolor}
\usepackage{hyperref}

\usepackage{enumitem}
\usepackage{wasysym}
\usepackage{geometry}
% Custom command for incorrect options
\newcommand{\incorrectOption}{\item[\textbf{\Circle}]}
% Custom command for correct option
\newcommand{\correctOption}{\item[\textbf{\CIRCLE}]}

\definecolor{darkgreen}{rgb}{0,0.8,0.3}
\definecolor{darkblue}{rgb}{0.00,0.00,0.55}


\begin{document}

\begin{center}
\rule{\textwidth}{.0075in} \\
\rule[3mm]{\textwidth}{.0075in}\\

Universidade do Algarve\hfill \textbf{Command Injection Attacks} \hfill 2024\\[3ex]

{\Large\bf Lab \#10} \\[3ex]

\begin{tabular}{l}
\textcolor{blue}{Email} \\ \hfill 
\end{tabular}
\begin{tabular}{l}
\textcolor{blue}{Due: Nov-26-2024 at 4:30PM} \\ \hfill 
\end{tabular}\\

\rule{\textwidth}{.0075in} \\
\rule[3mm]{\textwidth}{.0075in} \\
\end{center}

\section*{Injection Attacks}
Answer one (and only one) of the next questions following the last
digit of \textbf{your student number}. These questions were discussed
in class. The questions refer to \texttt{slides$\_$12} in Tutoria.

\begin{enumerate}
\item[0.] Slide 4. Why does allowing videos to be embedded in
  web-pages constitute a historical break-point for computer security?
  Amplify on what it was discussed in class. 
  %
\item Slide 4. What is the difference between bolt-on and built-in
  security? Amplify on what it was discussed in class.
  %
\item Slide 5. Regarding web server threats, what was discussed in
  class regarding ``compromise of underlying system''? Amplify on what
  it was discussed in class.
  %
\item Slide 7. What are the consequences of ``public access'' in web
  security? Amplify on what was discussed in class.
  %
\item Slide 8. Why is that web security is ``mission creep''? Amplify
  on what the slides says. 
  %
\item Slide 9. Why does this type of interface posse a security
  threat? Amplify on what it was discussed in class. 
  %
\item Slide 13. Why does this type of interface posse a security
  threat? Amplify on what it was discussed in class. 
  %
\item Slide 20, 21. What is the difference between static and dynamic
  content?  Amplify on what it was discussed in class. 
  %
\item Slide 26, 27. What type of problems (threats) do you see here? Amplify on what
  it was discussed in class. 
  %
\item Slide 29. What was discussed in class regarding ``control
  information'' versus ``data''? Explain. 
  
\end{enumerate}

\bigskip

\textbf{Your answer goes here}.


\end{document}
